Nobody expects the Spanish Inquisition: The effect of events on Australian parliamentary discussion

### 2018-09-22 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Update text modelling

```{r topicsoverdocuments, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over topics for two documents", fig.height = 3}
tibble(
  Topics = rep(c("1", "2", "3", "4", "5"), 2),
  Probability = c(c(0.40, 0.40, 0.1, 0.05, 0.05), c(0.01, 0.04, 0.35, 0.20, 0.4)),
  document = c(rep("Document 1", 5), rep("Document 2", 5))
  ) %>%
  ggplot(aes(Topics, Probability)) +
  geom_point() +
  theme_classic() +
  facet_wrap(vars(document), ncol = 2, scales = "free") +
  theme(strip.background = element_blank()) + 
  coord_flip()

@@

```{r topicsoverterms, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over terms", fig.height = 3}
tibble(
  Terms = rep(c("migration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"), 2),
  Probability = c(c(0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.2, 0.15, 0.4, 0.2), c(0.0142, 0.0142, 0.0142, 0.25, 0.35, 0.30, 0.0142, 0.0142, 0.0142, 0.0142)),
  Topics = c(rep("Topic 1", 10), rep("Topic 2", 10))
  ) %>%
  ggplot(aes(Terms, Probability)) +
  geom_point() +
  theme_classic() +
  facet_wrap(vars(Topics), ncol = 2, scales = "free") +
  theme(strip.background = element_blank()) + 
  coord_flip()

@@

The initial practical step when implementing LDA given a collection of documents is to remove 'stop words'. These are words that are common, but that don't typically help to define topics. There is a general list of stop words such as: "a"; "a's"; "able"; "about"; "above"... An additional list of words that are commonly found in Hansard, but likely don't help define topics is added to the general list. These additions include words such as: "act"; "amendment"; "amount"; "australia"; "australian"; "bill"... A full list can be found in Appendix \@ref(hansard-stop-word). We also remove punctuation and capitalisation. The documents need to then be transformed into a document-term-matrix. This is essentially a table with a column of the number of times each term appears in each document.

@@

## Structural Topic Model
### Overview and example
[TBD]

@@

# Summary and conclusions
What could happen if we had longer terms. Eg GST needed multiple generations of politicians but carbon tax couldn’t because it was one generation.

@@

@@

>>>>

```{r topicsoverdocuments, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over topics for two documents", fig.height = 4}

tibble(
  Topics = rep(c("1", "2", "3", "4", "5"), 2),
  Probability = c(c(0.40, 0.40, 0.1, 0.05, 0.05), c(0.01, 0.04, 0.35, 0.20, 0.4)),
  Document = c(rep("Document 1", 5), rep("Document 2", 5))
  ) %>%
  ggplot(aes(Topics, Probability, colour = Document)) +
  geom_point() +
  theme_classic() +
  coord_flip()  +
  scale_colour_viridis_d()

@@

```{r topicsoverterms, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over terms", fig.height = 4}
tibble(
  Terms = rep(c("migration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"), 2),
  Probability = c(c(0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.2, 0.15, 0.4, 0.2), c(0.0142, 0.0142, 0.0142, 0.25, 0.35, 0.30, 0.0142, 0.0142, 0.0142, 0.0142)),
  Topics = c(rep("Topic 1", 10), rep("Topic 2", 10))
  ) %>%
  ggplot(aes(Terms, Probability, colour = Topics)) +
  geom_point() +
  theme_classic() +
  coord_flip() +
  scale_colour_viridis_d()

@@

The initial practical step when implementing LDA given a collection of documents is to remove 'stop words'. These are words that are common, but that don't typically help to define topics. There is a common list of stop words such as: "a"; "an"; and "and". However the exact list used depends on research of focus. In the case of Australian Hansard, these are words such as: "australia"; "australian"; and "bill". Punctuation and capitalisation is also typically removed. The documents then need to then be transformed into a document-term-matrix. This is essentially a table with a column of the number of times each term appears in each document.

@@

## Structural Topic Model
The distinguishing aspect of the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 is that it includes additional information about documents. For instance, in general we usually have some information about the author and date of a document. In the case of Hansard, we know who was speaking and the date. STM allows this additional information to affect the construction of topics, though influencing either topical prevalence or topical content. That said, the assumption that there is some document generation process is the same as the LDA method, it is just that this process now includes metadata.

The STM is set-up to most easily include metadata to do with prevalence and content. Prevalence relates to the topic proportions in each document. For instance, we expect that topics related to the reasons for Federation such as tariffs and trade should be more prevalent in those earlier years than later. Similarly, we may expect topics to do with terrorism to be more prevalent in recent years than in earlier ones. Content relates to the words that make up each topic. For instance, there are changes in the use of language over the period for which we have data, and it would be better for these to not be responsible for defining different topics rather than being part of the same topic.

The document generation process of @Blei2003latent discussed earlier is modified slightly by @RobertsStewartAiroldi2016:

1. The proportion of a document dedicated to a topic is drawn "from a logistic-normal generalised linear model based on a vector of document covariates $X_d$":
$$\theta_d|X_d\gamma\sigma \sim logisticnormal(\mu = X_d\gamma, \sigma)$$
"where $X_d$ is a 1-by-p vector, $\gamma$ is a p-by-K - 1 matrix of coefficients and $\sigma$ is K-1 by K-1 covariance matrix." **THIS IS ALL QUOTES. NEED TO REWRITE.**
2. Given a document-level content covariate

HERE

1. There are  For each topic, decide the terms that the topic uses by randomly drawing distributions over the terms. The distribution over the terms for the $k$th topic is $\beta_k$. Typically a topic would be a small number of terms and so the Dirichlet distribution with hyperparameter $0<\eta<1$ is used: $\beta_k \sim \mbox{Dirichlet}(\eta)$.[^Dirichletfootnote] Strictly, $\eta$ is actually a vector of hyperparameters, one for each $K$, but in practice they all tend to be the same value.

STM can be implented using the stm R package of @RobertsStewartAiroldiRPackage.

@@

# Summary and conclusions
In this paper we examined

What could happen if we had longer terms. Eg GST needed multiple generations of politicians but carbon tax couldn’t because it was one generation.

@@

Future work - examine how it chagned during Federation

@@

| year | I have this number in Reps | They say this number in Senate | They say this number in Reps | Difference in Reps | Comment                          | Source                                                                                           |
|------|----------------------------|--------------------------------|------------------------------|--------------------|----------------------------------|--------------------------------------------------------------------------------------------------|
| 1902 | 106                        | 93                             | 107                          | 1                  | Positive means I am missing some | https://www.aph.gov.au/Parliamentary_Business/Statistics/Senate_StatsNet/General/sittingdaysyear |
| 1908 | 93                         | 84                             | 91                           | -2                 | Negative means I have too many   |                                                                                                  |
| 1909 | 97                         | 71                             | 98                           | 1                  |                                  |                                                                                                  |
| 1918 | 87                         | 68                             | 86                           | -1                 |                                  |                                                                                                  |
| 1920 | 113                        | 76                             | 114                          | 1                  |                                  |                                                                                                  |
| 1921 | 92                         | 79                             | 93                           | 1                  |                                  |                                                                                                  |
| 1934 | 36                         | 22                             | 35                           | -1                 |                                  |                                                                                                  |
| 1935 | 54                         | 37                             | 55                           | 1                  |                                  |                                                                                                  |
| 1942 | 44                         | 36                             | 45                           | 1                  |                                  |                                                                                                  |
| 1948 | 89                         | 39                             | 90                           | 1                  |                                  |                                                                                                  |
| 1951 | 55                         | 40                             | 56                           | 1                  |                                  |                                                                                                  |
| 1955 | 53                         | 36                             | 52                           | -1                 |                                  |                                                                                                  |
| 1974 | 64                         | 64                             | 62                           | -2                 |                                  |                                                                                                  |
| 1985 | 65                         | 74                             | 66                           | 1                  |                                  |                                                                                                  |
| 1991 | 66                         | 83                             | 67                           | 1                  |                                  |                                                                                                  |
| 1992 | 60                         | 76                             | 44                           | -16                |                                  |                                                                                                  |
| 1993 | 47                         | 53                             | 46                           | -1                 |                                  |                                                                                                  |
| 1994 | 69                         | 80                             | 68                           | -1                 |                                  |                                                                                                  |
| 1995 | 71                         | 78                             | 70                           | -1                 |                                  |                                                                                                  |
| 1997 | 79                         | 82                             | 76                           | -3                 |                                  |                                                                                                  |
| 1998 | 56                         | 57                             | 54                           | -2                 |                                  |                                                                                                  |
| 2000 | 71                         | 71                             | 73                           | 2                  |                                  |                                                                                                  |
| 2002 | 68                         | 60                             | 69                           | 1                  |                                  |                                                                                                  |
| 2003 | 74                         | 64                             | 75                           | 1                  |                                  |                                                                                                  |
| 2004 | 58                         | 49                             | 59                           | 1                  |                                  |                                                                                                  |
| 2012 | 63                         | 57                             | 67                           | 4                  |                                  |                                                                                                  |

### 2018-09-22 outputs/docs/events/svm-rmarkdown-article-example.tex
Update text modelling

\title{Nobody expects the Spanish Inquisition: The effect of events on
Australian parliamentary discussion \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful
suggestions. \textbf{Version as of}: September 20, 2018;
\textbf{Comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }

@@

The initial practical step when implementing LDA given a collection of
documents is to remove `stop words'. These are words that are common,
but that don't typically help to define topics. There is a general list
of stop words such as: ``a''; ``a's''; ``able''; ``about'';
``above''\ldots{} An additional list of words that are commonly found in
Hansard, but likely don't help define topics is added to the general
list. These additions include words such as: ``act''; ``amendment'';
``amount''; ``australia''; ``australian''; ``bill''\ldots{} A full list
can be found in Appendix \ref{hansard-stop-word}. We also remove
punctuation and capitalisation. The documents need to then be
transformed into a document-term-matrix. This is essentially a table
with a column of the number of times each term appears in each document.

@@

\subsubsection{Overview and example}\label{overview-and-example}

@@

@@

>>>>

\title{Nobody expects the Spanish Inquisition: The effect of events on
Australian parliamentary discussion \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
Wang, Matt Jacob, Leslie Root, Jill Sheppard and Matthew Kerby for their
helpful suggestions. \textbf{Version as of}: September 22, 2018;
\textbf{Comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }

@@

The initial practical step when implementing LDA given a collection of
documents is to remove `stop words'. These are words that are common,
but that don't typically help to define topics. There is a common list
of stop words such as: ``a''; ``an''; and ``and''. However the exact
list used depends on research of focus. In the case of Australian
Hansard, these are words such as: ``australia''; ``australian''; and
``bill''. Punctuation and capitalisation is also typically removed. The
documents then need to then be transformed into a document-term-matrix.
This is essentially a table with a column of the number of times each
term appears in each document.

@@

The distinguishing aspect of the Structural Topic Model (STM) of
\citet{RobertsStewartAiroldi2016} is that it includes additional
information about documents. For instance, in general we usually have
some information about the author and date of a document. In the case of
Hansard, we know who was speaking and the date. STM allows this
additional information to affect the construction of topics, though
influencing either topical prevalence or topical content. That said, the
assumption that there is some document generation process is the same as
the LDA method, it is just that this process now includes metadata.

The STM is set-up to most easily include metadata to do with prevalence
and content. Prevalence relates to the topic proportions in each
document. For instance, we expect that topics related to the reasons for
Federation such as tariffs and trade should be more prevalent in those
earlier years than later. Similarly, we may expect topics to do with
terrorism to be more prevalent in recent years than in earlier ones.
Content relates to the words that make up each topic. For instance,
there are changes in the use of language over the period for which we
have data, and it would be better for these to not be responsible for
defining different topics rather than being part of the same topic.

The document generation process of \citet{Blei2003latent} discussed
earlier is modified slightly by \citet{RobertsStewartAiroldi2016}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The proportion of a document dedicated to a topic is drawn ``from a
  logistic-normal generalised linear model based on a vector of document
  covariates \(X_d\)'':
  \[\theta_d|X_d\gamma\sigma \sim logisticnormal(\mu = X_d\gamma, \sigma)\]
  ``where \(X_d\) is a 1-by-p vector, \(\gamma\) is a p-by-K - 1 matrix
  of coefficients and \(\sigma\) is K-1 by K-1 covariance matrix.''
  \textbf{THIS IS ALL QUOTES. NEED TO REWRITE.}
\item
  Given a document-level content covariate
\end{enumerate}

HERE

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  There are For each topic, decide the terms that the topic uses by
  randomly drawing distributions over the terms. The distribution over
  the terms for the \(k\)th topic is \(\beta_k\). Typically a topic
  would be a small number of terms and so the Dirichlet distribution
  with hyperparameter \(0<\eta<1\) is used:
  \(\beta_k \sim \mbox{Dirichlet}(\eta)\).\footnote{The Dirichlet
    distribution is a variation of the beta distribution that is
    commonly used as a prior for categorical and multinomial variables.
    If there are just two categories, then the Dirichlet and the beta
    distributions are the same. In the special case of a symmetric
    Dirichlet distribution, \(\eta=1\), it is equivalent to a uniform
    distribution. If \(\eta<1\), then the distribution is sparse and
    concentrated on a smaller number of the values, and this number
    decreases as \(\eta\) decreases. A hyperparameter is a parameter of
    a prior distribution.} Strictly, \(\eta\) is actually a vector of
  hyperparameters, one for each \(K\), but in practice they all tend to
  be the same value.
\end{enumerate}

STM can be implented using the stm R package of
\citet{RobertsStewartAiroldiRPackage}.

@@

In this paper we examined

@@

\begin{longtable}[]{@{}lllllll@{}}
\toprule
\begin{minipage}[b]{0.02\columnwidth}\raggedright\strut
year\strut
\end{minipage} & \begin{minipage}[b]{0.09\columnwidth}\raggedright\strut
I have this number in Reps\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright\strut
They say this number in Senate\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright\strut
They say this number in Reps\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\raggedright\strut
Difference in Reps\strut
\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\raggedright\strut
Comment\strut
\end{minipage} & \begin{minipage}[b]{0.31\columnwidth}\raggedright\strut
Source\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1902\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
106\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
93\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
107\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
Positive means I am missing some\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\url{https://www.aph.gov.au/Parliamentary_Business/Statistics/Senate_StatsNet/General/sittingdaysyear}\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1908\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
93\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
84\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
91\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-2\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
Negative means I have too many\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1909\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
97\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
71\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
98\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1918\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
87\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
68\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
86\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1920\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
113\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
76\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
114\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1921\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
92\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
79\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
93\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1934\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
36\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
22\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
35\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1935\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
54\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
37\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
55\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1942\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
44\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
36\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
45\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1948\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
89\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
39\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
90\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1951\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
55\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
40\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
56\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1955\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
53\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
36\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
52\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1974\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
64\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
64\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
62\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-2\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1985\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
65\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
74\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
66\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1991\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
66\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
83\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
67\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1992\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
60\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
76\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
44\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-16\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1993\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
47\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
53\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
46\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1994\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
69\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
80\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
68\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1995\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
71\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
78\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
70\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1997\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
79\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
82\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
76\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-3\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
1998\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
56\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
57\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
54\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-2\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
2000\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
71\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
71\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
73\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
2\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
2002\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
68\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
60\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
69\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
2003\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
74\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
64\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
75\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
2004\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
58\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
49\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
59\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
1\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
2012\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
63\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
57\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
67\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
4\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}
